My title

### 2024-03-31 paper/paper.qmd
update sub-data for model analysis

```{r}
#| label: tbl-data-overview
#| tbl-cap: Overview of the Categorized Data 
#| echo: false
#| warning: false
#| message: false

kable(demo_data,row.names = FALSE)|>
  kable_styling() |>
  row_spec(6, hline_after = TRUE)
```

@@

@@

```{r}
#| label: fig-demo-physical
#| fig-cap: Gender and Age of People Apprehended Visulization Year-Depended
#| fig-subcap: ["Gender","Age cohorts"]
#| layout-ncol: 2
#| echo: false
#| warning: false
#| message: false

@@

>>>>

@@

## Demographic Variables 
```{r}
#| label: tbl-data-overview
#| tbl-cap: Overview of the Demographic Data 
#| echo: false
#| warning: false
#| message: false

vars <- c("ID","Gender","Age","Physical Unwellness","Mental Unwellness","Age Cohort")

kable(head(demo_data), 
      caption = "Counted days of Physical and Mental unwellness of Population by Age and Gender Group", 
      align = "c",
      col.names = vars,
      row.names = FALSE) |>
  kable_styling(latex_options = c("striped", "hold_position"), bootstrap_options = "striped", full_width = FALSE)
```

@@

@@

```{r}
#| label: fig-demo-physical
#| fig-cap: Gender and Age of People Apprehended Visulization Year-Depended22
#| fig-subcap: ["Gender","Age cohorts"]
#| layout-ncol: 2
#| echo: false
#| warning: false
#| message: false
